Assessing Usability of Tor Browser

### 2015-04-10 PETS2015-paper/paper.tex
merging stuff
dash

\begin{abstract}
Our talk will be about ongoing experiments aimed at
assessing and improving the usability of Tor Browser.
There have been been no major usability evaluations of
Tor Browser since the introduction of the 4.0 series,
which introduced radical UI changes.
We will briefly describe the results of a completed study
that examined downloading and installing the browser
and using it for basic browsing tasks.
This study uncovered a number of bugs and stopping points
and has already effected concrete change in the browser.
We will describe our plans for future studies aimed at
isolating specific browser features in depth,
with a detailed design of an experiment to evaluate
Tor Browser as a tool for censorship circumvention.
{\color {red}LL: I don't know how to say this, but I want the fact that we are evaluating it from a different standpoint --ie as a censorship circumvention tool, to stand out more. Also, we spend more abstract real estate talking about the first experiment rather than our design, which I think should be flipped. But for right now, I can't think of what exactly to fix so I'll look at this later.}
We solicit feedback on our experimental design
and the specific features of the browser that we are testing.
\end{abstract}

@@

%moved this up to this new section 
After our first experiment, it was clear to us that so many of the features had been left uninvestigated--such as advanced web browsing tasks, the configuration menu, (what else were we going to investigate?), etc. But rather than selecting the features to study in isolation, we decided to study the new context in which the Tor browser is being used, censorship circumvention. To our knowledge, this is the first user study investigating the usability of Tor as a censorship circumvention tool, rather than an anonymity tool.

@@

@@

\begin{itemize} \itemsep1pt \parskip0pt \parsep0pt
\item{Corporate network.}
A simulation of a corporate or educational firewall.
Blocks all services but HTTP, HTTPS, and DNS.
Certain non-work-related domains, like youtube.com and torproject.org,
are blocked by DNS and HTTP inspection.
Blocked requests are redirected to a block page.
\item{DNS-only censor.}
This censor injects false replies to DNS queries
for forbidden domain names (DNS poisoning),
but does not do deep packet inspection on TCP streams.
Unlike the corporate censor, this censor allows protocols
other than HTTP, HTTPS, and DNS.
\item{Comprehensive censor.}
Employs a variety of techniques, depending on the target.
May do DNS poisoning, IP blocking, and inspection of TCP streams
(examining the URL of HTTP requests, for example).
Some domains may be blocked by DNS and deep packet inspection;
others may additionally be blocked by IP address.
Tor relays are blocked by IP address.
Some domains, like wikipedia.org, may allow HTTP but not HTTPS.
Blocked requests fail silently (no block page).
\end{itemize}

\noindent {\bfseries List of Tasks} 
We will divide our participants into treatments
by censorship environment.
All participants will be asked to complete the same
list of tasks.
We constructed the list by looking at some of the top
Alexa sites and imagining what might be reasonable
and relevant tasks for each
(that do not require a participant to reveal private information
like passwords).
The tasks are not all intended to be challenging to complete.

>>>>

\begin{abstract}
Our talk will be about ongoing experiments aimed at
assessing and improving the usability of Tor Browser.
There have been been no major usability evaluations of
Tor Browser since the introduction of the 4.0 series,
which introduced radical UI changes.
We briefly describe the results of a completed study
that examined the download, install, and 
and basic browsing behaviors.
This study uncovered a number of bugs and stopping points
and has already effected concrete change in the browser.
We will describe a future study aimed at
evaluating Tor Browser as a tool for censorship circumvention, isolating specific browser features in depth in the process. 
{\color {red}LL: I don't know how to say this, but I want the fact that we are evaluating it from a different standpoint --ie as a censorship circumvention tool, to stand out more. Also, we spend more abstract real estate talking about the first experiment rather than our design, which I think should be flipped. But for right now, I can't think of what exactly to fix so I'll look at this later.}
We solicit feedback on our experimental design
and the specific features of the browser that we are testing.
\end{abstract}

@@

%moved this up to this new section 
After our first experiment, it was clear to us that so many of the features had been left uninvestigated---such as advanced web browsing tasks, the configuration menu, (what else were we going to investigate?), etc. But rather than selecting the features to study in isolation, we decided to study the new context in which the Tor browser is being used, censorship circumvention. To our knowledge, this is the first user study investigating the usability of Tor as a censorship circumvention tool, rather than an anonymity tool.

@@

\begin{itemize} \itemsep1pt \parskip0pt \parsep0pt
\item{Corporate network.}
A simulation of a enterprise or educational firewall.
Blocks all services but HTTP, HTTPS, and DNS.
Certain non-work-related domains, like youtube.com and torproject.org,
are blocked by DNS and HTTP inspection.
Blocked requests are redirected to a block page.
\item{DNS-only censor.}
This censor injects false replies to DNS queries
for forbidden domain names (DNS poisoning),
but does not do deep packet inspection on TCP streams.
Unlike the corporate censor, this censor allows protocols
other than HTTP, HTTPS, and DNS.
\item{Comprehensive censor.}
Employs a variety of techniques, depending on the target.
May do DNS poisoning, IP blocking, and inspection of TCP streams
(examining the URL of HTTP requests, for example).
Some domains may be blocked by DNS and deep packet inspection;
others may additionally be blocked by IP address.
Tor relays are blocked by IP address.
Some domains, like wikipedia.org, may allow HTTP but not HTTPS.
Blocked requests fail silently (no block page).
\end{itemize}

\noindent {\bfseries List of Tasks} 
The lists of tasks were originally inspired by the top Alexa sites, which gave an idea of relevant and popular browsing behavior, then refined by ethical concerns, filtering out tasks which would require a participant to reveal private information. The resulting task list is one which we hope is both representative of how a user might browse the internet, but also give good coverage of sites which are censored today.

All participants will be asked to complete the same list of tasks, regardless of the censorship environment. Although every participant will attempt the same set of tasks, the difficulty of completing these tasks will vary on their chosen censorship environment. The tasks are not all intended to be challenging to complete. Some may not even require the use or Tor Browser, depending on the environment.

@@
